### 2013-02-08 doc/icml2013/algo.tex

Recovery of $B$, $\mathcal{B}$.

Use AHK2012

Lemma error of $B$.

Lemma AHK2012 error

Theorem on polynomial recovery

>>>>

An overview of the algorithm is as follows; use low-rank/ridge regression recovery techniques to recover the $B$ and $\mathcal{B}$ from moments of the data. Use the tensor factorization to recover the $\pi$, $\beta$ which are eigenvalues/eigenvectors.

\begin{theorem}
  Recovery analysis of mixture of linear regressions.
\end{theorem}
\begin{proof}
\end{proof}

\subsection{Recovering $B$ and $\mathcal{B}$}

Writing out the regression problem.

\begin{lemma}
  Recovery analysis of ridge regression is $\le \Omega(\frac{d^2}{n})$.
  Try and figure out dependence on condition numbers. It's similarly
  $\le \Omega(\frac{d^3}{n})$.
\end{lemma}
\begin{proof}
  Theorem X \cite{HsuKakadeZhang2011}.
\end{proof}

Using low-rank gradient methods. Overview SVD for

\begin{lemma}
  Recovery analysis of nuclear-norm regression is $\le
  \Omega(\frac{kd}{n})$. Try and figure out dependence on condition
  numbers.
\end{lemma}
\begin{proof}
  Theorem X \cite{NegahbanWainwright2009}.
  Theorem Y \cite{Tomioka2011}.
\end{proof}

\subsection{Recovering Regression Coefficients}

Write out the form of $B$ and $\mathcal{B}$ in symmetric tensor form.

Use Tensor Power Method to recovery $\beta_k$.

\begin{lemma}
  Bound error in the $\beta$ based on the errors of $B$ and $\mathcal{B}$.
\end{lemma}
\begin{proof}
  \cite{AnandkumarGeHsu2012}
\end{proof}

### 2013-02-08 doc/icml2013/model.tex
minor changes

Mixture of Experts

@@

>>>>

\newcommand{\xn}[1]{x^{(#1)}}
\newcommand{\xni}{\xn{i}}
\newcommand{\yn}[1]{y^{(#1)}}
\newcommand{\yni}{\yn{i}}

The mixture of linear regressions model describes response variables $y
\in \Re$ dependent on covariates $x \in \Re^d$ through $K$ different
modes. In particular, each mode occurs with a fixed probability of
$\pi_k$, and each mode is independently described by regression
coefficients $\beta_k$, with a common variance $\sigma^2$. Formally, the
generative process is,
\begin{eqnarray}
  z &\sim& \mult(\pi) \\
  y | z = k &\sim& \normal{ \beta_{k}^T x, \sigma^2 }.
\end{eqnarray}

We would like to recover $B = [\beta_1 | \beta_2 | \cdots | \beta_K]$
and the mixture probabilities $\pi = [\pi_1 | \pi_2 | \cdots | \pi_K]$.

\subsection{Non-linearities}

Approach to handle non-linearities.

Note about dependencies in the n-th moments.

@@

The model is in general identifiable, except for a pathological case
with how data points are placed.

Plot of the above scenario.

Interesting question; how do these extend in the non-linear case (which
would be ``new'').
